Portfolios of Subgraph Isomorphism Algorithms

### 2015-12-12 paper/paper.tex
clarify results for different timeouts

The results show that while for the misclassification penalty, LLAMA is always
better than the single best algorithm, for timeouts $10^2$ to $10^4$ it is worse
in terms of the number of solved instances and mean performance. An explanation
for this is that empirical runtime measurements are inherently noisy, which
affects the accuracy of the measurements particularly in this range.

>>>>

The results show that while for the misclassification penalty, LLAMA is always
better than the single best algorithm, for timeouts $10^2$ to $10^4$ it is worse
in terms of the number of solved instances and mean performance. The
misclassification penalty does not take the cost of computing features into
account, while the mean performance does -- for these small timeouts, the cost
of computing the features dominates any improvement through algorithm selection.
Another explanation for this is that empirical runtime measurements are
inherently noisy, which affects the accuracy of the measurements and hence the
performance of the algorithm selection models particularly in this range.
